### 2022-01-10 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@026deab5c8025bdff8bbbfe770cdde8d08049f2d 🚀

In this section, we will assume a network of connectance \(\rho\),
\emph{i.e.} having \(\rho S^2\) interactions (where \(S\) is the species
richness), and \((1-\rho) S^2\) non-interactions. Therefore, the vector
describing the \emph{true} state of the network (assumed to be an
unweighted, directed network) is a column vector
\(\mathbf{o}^T = [\rho (1-\rho)]\) (we can safely drop the \(S^2\)
terms, as we will work on the confusion matrix, which ends up expressing
\emph{relative} values). We will apply skill and bias to this matrix,
and measure how a selection of performance metrics respond to changes in
these values, in order to assess their suitability for model evaluation.

@@

In order to write the values of the confusion matrix for a hypothetical
classifier, we need to define two characteristics: its skill, and its
bias. Skill, here, refers to the propensity of the classifier to get the
correct answer (\emph{i.e.} to assign interactions where they are, and
to not assign them where they are not). A no-skill classifier guesses at
random, \emph{i.e.} it will guess interactions with a probability
\(\rho\). The predictions of a no-skill classifier can be expressed as a
row vector \(\mathbf{p} = [\rho (1-\rho)]\). The confusion matrix
\(\mathbf{M}\) for a no-skill classifier is given by the element-wise
product of these vectors \(\mathbf{o} \odot \mathbf{p}\), \emph{i.e.}

>>>>

In this section, we will assume a network of connectance \(\rho\),
\emph{i.e.} having \(\rho S^2\) interactions (where \(S\) is the species
richness), and \((1-\rho) S^2\) non-interactions. Therefore, the vector
describing the \emph{true} state of the network (assumed to be an
unweighted, directed network) is a column vector
\(\mathbf{o}^T = [\rho, (1-\rho)]\) (we can safely drop the \(S^2\)
terms, as we will work on the confusion matrix, which ends up expressing
\emph{relative} values). We will apply skill and bias to this matrix,
and measure how a selection of performance metrics respond to changes in
these values, in order to assess their suitability for model evaluation.

@@

In order to write the values of the confusion matrix for a hypothetical
classifier, we need to define two characteristics: its skill, and its
bias. Skill, here, refers to the propensity of the classifier to get the
correct answer (\emph{i.e.} to assign interactions where they are, and
to not assign them where they are not). A no-skill classifier guesses at
random, \emph{i.e.} it will guess interactions with a probability
\(\rho\). The predictions of a no-skill classifier can be expressed as a
row vector \(\mathbf{p} = [\rho (1-\rho)]\). The confusion matrix
\(\mathbf{M}\) for a no-skill classifier is given by the element-wise
(Hadamard, outer) product of these vectors
\(\mathbf{o} \odot \mathbf{p}\), \emph{i.e.}
